Austraits -- a curated plant trait database for the Australian flora

### 2019-04-29 ms.Rmd
Figure 3 caption

>>>>

![**Figure 3.** The phylogenetic representation of traits in the AusTraits database for the subset of 2000 randomly sampled species. The heatmap colour intensities denote the number of traits measured within each major plant organ. The most widespread family names (with more than ten species) are labelled on the edge of the tree.](figures/austraits_phlogenetic_coverage.png)

<!-- Cite: -->
  <!-- G Yu, DK Smith, H Zhu, Y Guan, TTY Lam*. ggtree: an R package for visualization and annotation of phylogenetic trees with their covariates and other associated data. Methods in Ecology and Evolution. 2017, 8(1):28-36. doi: 10.1111/2041-210X.12628.  -->
  <!-- G Yu*, TTY Lam, H Zhu, Y Guan*. Two methods for mapping and visualizing associated data on phylogeny using ggtree. Molecular Biology and Evolution, 2018, 35(2):3041-3043. doi: 10.1093/molbev/msy194. -->
